---
title: "Eating Out"
author: "Jared Lobitana"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

In this analysis we're gonna identify the difference in each ethnicity about the frequency of eating out. We will find the significance of these each ethnicity in this analysis.


## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
#race = c ("white","black","other")
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Method

The method that we will be using is cat~num, The variable will be Race ~ frequency of eating out.

# Results

## Descriptive Results



### Graphical Results

```{r}
barchartGC(~race+ eatout,data=mydata)
barchartGC(~race + eatout,data=mydata,type="percent")
```

These graphs suggests that there is a small differnce between the ethnicity eating out. 

## Numerical description

```{r}
table1 <- xtabs (~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
The results in this numerical description sheet shows the frequency of eating out in white ethnicity as opposed to black and other ethnicity. The table shows that frequency of white ethnicity eating out is more than black and other ethnicities. 

### Inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Chi squared result in the p-value between white and balck is 0.0008179. We see the number is too small that’s why we reject the null hypothesis. Chi squared result between the white and other the p-value 0.3534. We see that there’s no difference which is that’s why we failed to reject the null hypothesis. Chi squared result between black and other the p-value 0.2815. We see that there’s no difference that’s why we failed to reject the null hypothesis.

# Discussion and Conclusion

Based on the results, we reject the null hypothesis because the p-value is so small, 0.0008179, concluding that there is a difference in the frequency of eating out based on race. 
